working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2018-12-12 Manuscript_draft/Manuscript_draft.tex
edits for Nacho´s meeting

\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
\usepackage{graphicx}
% Redefine \includegraphics so that, unless explicit options are
% given, the image width will not exceed the width of the page.
% Images get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\ScaleIfNeeded{%
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother
\let\Oldincludegraphics\includegraphics
{%
 \catcode`\@=11\relax%
 \gdef\includegraphics{\@ifnextchar[{\Oldincludegraphics}{\Oldincludegraphics[width=\ScaleIfNeeded]}}%
}%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

@@

\title{working title Compatibility system and stygma size of pollen recipient
as main predictors of heterospecific pollen effect}
\author{
Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader
}
\date{}
% Allowing for landscape pages
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

@@

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge working title Compatibility system and stygma size of pollen recipient
as main predictors of heterospecific pollen effect
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader \textsuperscript{*} \textsuperscript{1,2,3} 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}US Environmental Protection Agency, Office of Research and Development,
National Health and Environmental Effects Research Laboratory, Atlantic
Ecology Division, 27 Tarzwell Drive Narragansett, RI, 02882, USA\\*
\\*
\textsuperscript{2}Big Name University, Department of R, City, BN, 01020, USA\\*
\\*
\textsuperscript{3}Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

@@

Pollinator sharing can have negative consequences for species fitness
with the arrival of foreign pollen. However, the costs of heterospecific
pollen are not yet well understood. For this reason, we have conducted a
glasshouse experiment where we try to understand how phylogenetic
relatedness and the different traits of these species are involved in
this process. We experimentally crossed 10 species belonging to three
different families: Brassicaceae, Solanaceae and Convolvulaceae.
Overall, more than 4000 crosses were done and seed set and pollen tubes
were considered as proxy of effect. We found that for all species
foreign pollen (50\% or less) reduced seed set. Moreover, the seed set
reduction is not dependent on the degree of relatedness of the pollen
donor. However, the effect is governed by the degree of relatedness and
the traits of the species recipient. Our results show that the outcome
of heterospecific pollen deposition is determined in greater degree by
the traits of the pollen recipient than the pollen donor and that
certain traits such as compatibility system are crucial to understand
the costs of heterospecific pollen.

\vspace{3mm}\hrule

@@

By visiting many plant species, many pollinators are responsible for
conspecific pollen loss and the transport of foreign pollen, both of
which can have important detrimental effects on species fitness Morales
and Traveset (2008); Ashman and Arceo-Gómez (2013); Arceo-Gómez and
Ashman (2016). Foreign pollen arrival can play an important role in
plant species fitness but outcomes are variable and appear to be context
dependent as there is not always a decrease in fitness Morales and
Traveset (2008). Some of this variation is likely due to the enormous
variability of foreign pollen transferred across systems ranging from
between 0 and 75 percent but most studies report ranges of
heterospecific pollen between 0 and 20 percent of the total pollen load
Bartomeus et al. (2008) Montgomery and Rathcke (2012); Ashman and
Arceo-Gómez (2013); Fang and Huang (2013), yet even these relatively low
amounts of heterospecific pollen transferred can decrease fitness
greatly Thomson et al. (1982). While we now have some understanding of
the impacts of heterospecific pollen quantity, we have less
understanding of other factors that could be driving the variation in
impacts upon fitness. Ashman and Arceo-Gómez (2013) postulated the first
predictive framework that identifies a need to understand how plant
traits might mediate heterospecific pollen effect, whereby mating system
and pollen size were predicted to potentially mediate the impact of
foreign pollen transfer on plant fitness. This concept is supported by
other studies, such as Tong and Huang (2016) that demonstrate an
asymmetrical effect in 6 species of Pedicularis whereby the pollen of
long styled species was able to grow the full length of the style on
short styled species but not vice versa. While this suggests that the
impacts of heterospecific pollen may differ among pollen donor and
recipient, few studies have been conducted to ascertain whether this
pattern is in fact a trend or to identify the extent to which other
plant traits are critical to heterospecific pollen impacts.

@@

Given the large variability in mating systems across populations
Whitehead et al. (2018), it is difficult to determine potential impacts
upon HP transfer yet incompatibility system is another plant trait that
appears to play an important role in foreign pollen effect whereby
species that are self incompatible have stronger barriers to
heterospecific pollen than self-compatible species Ashman and
Arceo-Gómez (2013). The type of incompatibility, (i.e.~whether
sporophytic or gametophytic) is related to the location of pollen
recognition; sporophytic incompatibility relates to signaling at the
stigma surface while gametophytic occurs within the style. This later
acting pollen recognition mechanism is associated with greater negative
effect than sporophytic recognistion Barrett (1988). Nonetheless, an
effect of foreign pollen is a bit obscured by the variability within
species, however species that are strong selfers or strong outcrossers
have less variablity in mating systems and predictions of effect could
be more realistic (see figure 1 from Whitehead et al. (2018)). Moreover,
other traits such as number of pollen grains per flower and number of
ovules have been traditionally associated with the type of
incompatibility system where species with higher pollen ovule ratios are
predicted to be xenogamous and species with low pollen ovule ratios
autogamous (REF). Selfer species are known to have a reduction of
herkogamy (REF) and less pollen production per ovule (REF) which can be
interpretated as a reduction of pollen exported into the community.
Other morphological traits, like stigma size can be determinant for the
total pollen quatity that a stigma can receive and therefore related to
do that pollen size would also play an important role. Example with
pollen here.

\textbf{Paragraph 3} Maybe connect with paragrph above?

Species with similar traits are more closely related XXXXXXXXX. (Refs?
Brown and Mitchell (2001) Arceo-Gómez et al. (2016) Tong and Huang
(2016) ). Several studies predict that the impact of HP transfer is
likely to be greater for closely related species (Ashman and Arceo-Gómez
(2013)). Few studies however, have focused on the impacts of
heterospecific pollen of distantly related species Thomson et al. (1982)
Galen and Gregory (1989) Neiland and Wilcock (1999). Yet, most insects
and most stigmas have been found to carry multiple species of foreign
pollen with little attention to degree of relatedness (Arceo-Gómez and
Ashman (2016); Fang and Huang (2013) ; also cite studies from pollen
transfer networks here such as ). Further, a majority of plant species
are generalist and thus receive visits from multiple different
pollinators. Given these are generally the ones that receive greater
loads of heterospecific pollen Fang and Huang (2013) and unrelated
species are more likely to coexist with other species due to less niche
overlap (Ref), understanding the role of foreign pollen from distantly
related species thus deserves greater attention in understanding
coexistence blah blahXXXXX refs.. Notwithstanding, the effect of
heterospecific pollen of far and close related species at community
level remains to be explored beyond single pairwise interactions.

\textbf{Paragraph 4} Introducing our experiment

@@

We used the statistical language \texttt{R} (R Core Team 2018) for all
our analyses. To test the effect of heterospecific pollen, we
substracted to the seed set of hand cross pollination the seed set of
heterospecific pollen treatments. Therefore, small values mean low
effect and viceversa. To be able to compare among species, seed set was
previosly scaled with mean 0 and standard deviation of 1. In order to
see correlations between hetereospecific pollen effect and traits we
performed Mantel test between the matrix of effect and the distance
matrix of each trait (euclidean distances). Moreover, Mantel test was
also conducted between heterospecific pollen effect and the square root
of the matrix of phylogenetic distance due to improvement in the
statistical power (Letten \& Cornwell 2014). We explored also the the
relations between traits and heterospecific pollen effect through
generalized mixed models where the response variable was heterospecific
pollen effect, the independent variable the different traits and the
random effects the different treatments per species. Moreover, pairwise
evolutive distances were calculated with MEGA7 for two kinds of markers:
1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate
carboxylase (RBCL). The sequences of interest were downloaded from NCBI
GenBank and the phylogenetic tree constructed by maximum likelihood with
MEGA7.

Phylogenetic signal of traits?

@@

Results of hand cross pollination, self hand pollination, natural
selfing and apomixis are presented in \textbf{Table 2}. Heterospecific
pollen reduced seet set signifcatively with the 50-50\% heterospecific
pollen treatments for 65\% of the pairwise interactions
p\textless{}0.05. Across families we found a very similar effect but
when species where look at species level they respond differently even
within the same family, for instance for two species of the Brassicaceae
family \emph{Brassica oleracea} and \emph{Eruca versicaria} we found
very contrasting effects of foreign pollen where for the first one, all
donors reduce seed set significatively and for the second, just two
species did out of nine. The 100\% foreign pollen treatments barely
produced seeds or fruits and just for \emph{Sinapis alba} we did not
find significant differences between the hand cross pollination and one
treatment with pollen from a confamilial. Solanaceae species with berry
fruit type developed small fruits or even normal fruits in some cases.
\emph{S. lycopersicum} seems to produced small fruits (35\% of the
treatments) independently of pollen and pollen donor due to also
apomictic treatments did, never normal size. \emph{C. annuum} produced
some fruits (9\%) of both small and normal size and finally \emph{S.
melongena} produced seedless normal fruits with just confamilial pollen
(3\%), for both species seems that fruit formation was induced by pollen
on the stigma because of lack of fruit production with apomictic
treatments.

@@

Mantel test indicates that a possible correlation exist between
heterospecific pollen effect and the evolutive distances, for ITS and
RBCL markers we had r coefficients of 0.29 and 0.25 respectively
p\textless{}0.05. Moreover, Mantel test indicates that also a possible
correlation between stigma width and stigma type exist. Trait
correlations were also explored with \ldots{} and we found that\ldots{}

Fix mantel test selfing rates and change it for compatibility
index\ldots{}

Fix this to GLMM? Yep I have to\ldots{}

@@

@@

@@

\emph{Negative}

-Stigma clogging

\begin{itemize}
\item
\end{itemize}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
\usepackage{graphicx}
% Redefine \includegraphics so that, unless explicit options are
% given, the image width will not exceed the width of the page.
% Images get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\ScaleIfNeeded{%
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother
\let\Oldincludegraphics\includegraphics
{%
 \catcode`\@=11\relax%
 \gdef\includegraphics{\@ifnextchar[{\Oldincludegraphics}{\Oldincludegraphics[width=\ScaleIfNeeded]}}%
}%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

@@

\title{working title Compatibility system and stigma size are the main
predictors of heterospecific pollen effect}
\author{
Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader
}
\date{}
% Allowing for landscape pages
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

@@

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge working title Compatibility system and stigma size are the main
predictors of heterospecific pollen effect
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader \textsuperscript{*} \textsuperscript{1,2,3} 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}US Environmental Protection Agency, Office of Research and Development,
National Health and Environmental Effects Research Laboratory, Atlantic
Ecology Division, 27 Tarzwell Drive Narragansett, RI, 02882, USA\\*
\\*
\textsuperscript{2}Big Name University, Department of R, City, BN, 01020, USA\\*
\\*
\textsuperscript{3}Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

@@

Pollinator sharing can have negative consequences for plant fitness with
the arrival of foreign pollen. However, the costs of heterospecific
pollen are not yet well understood. We conducted a glasshouse experiment
to understand how phylogenetic relatedness and plant traits mediate the
impacts of heterospecific pollen transfer. We conducted 4XXXX crosses by
experimentally transferring pollen (50\% and 100\% ratio) with
reciporcal crosses between 10 species belonging to three different
families: Brassicaceae, Solanaceae and Convolvulaceae. Seed set was used
as proxy of plant fitness. We found that for 65\% of the treatments with
50\% mix reduced seed set. Moreover, the reduction in seed set was
dependent on the degree of relatedness and reproductive traits of the
pollen recipient and not the pollen donor. Our results show that certain
traits, particularly compatibility system, are critical in understanding
the costs of heterospecific pollen. \vspace{3mm}\hrule

@@

By visiting many plant species, many pollinators are responsible for
conspecific pollen loss and the transport of foreign pollen, both of
which can have important detrimental effects on species fitness Morales
and Traveset (2008); Ashman and Arceo-Gómez (2013); Arceo-Gómez and
Ashman (2016). Foreign pollen arrival can play an important role in
plant species fitness but outcomes are variable and appear to be context
dependent as there is not always a decrease in fitness Morales and
Traveset (2008). Some of this variation is likely due to the enormous
variability of foreign pollen transferred across systems ranging from
between 0 and 75 percent but most studies report ranges of
heterospecific pollen between 0 and 20 percent of the total pollen load
Bartomeus et al. (2008) Montgomery and Rathcke (2012); Ashman and
Arceo-Gómez (2013); Fang and Huang (2013), yet even these relatively low
amounts of heterospecific pollen transferred can decrease fitness
greatly Thomson et al. (1982). While we now have some understanding of
the impacts of heterospecific pollen quantity, we have less
understanding of other factors that could be driving the variation in
impacts upon fitness. Ashman and Arceo-Gómez (2013) postulated the first
predictive framework that identifies a need to understand how plant
traits might mediate heterospecific pollen effect, whereby mating system
and pollen size were predicted to potentially mediate the impact of
foreign pollen transfer on plant fitness. This concept is supported by
other studies, such as Tong and Huang (2016) that demonstrate an
asymmetrical effect in 6 species of \emph{Pedicularis} whereby the
pollen of long styled species was able to grow the full length of the
style on short styled species but not vice versa. While this suggests
that the impacts of heterospecific pollen may differ among pollen donor
and recipient, few studies have been conducted to ascertain whether this
pattern is in fact a trend or to identify the extent to which other
plant traits are critical to heterospecific pollen impacts.

@@

Given the large variability in mating systems across populations
Whitehead et al. (2018), it is difficult to determine potential impacts
upon HP transfer yet incompatibility system is another plant trait that
appears to play an important role in foreign pollen effect whereby
species that are self incompatible have stronger barriers to
heterospecific pollen than self-compatible species Ashman and
Arceo-Gómez (2013). The type of incompatibility, (i.e.~whether
sporophytic or gametophytic) is related to the location of pollen
recognition; sporophytic incompatibility relates to signaling at the
stigma surface while gametophytic occurs within the style Barrett
(1988). This later acting pollen recognition mechanism is associated
with greater negative effect than sporophytic recognistion Ashman and
Arceo-Gómez (2013). Nonetheless, an effect of foreign pollen is a bit
obscured by the variability within species, however species that are
strong selfers or strong outcrossers have less variablity in mating
systems and predictions of effect could be more realistic (see figure 1
from Whitehead et al. (2018)). Moreover, other traits such as number of
pollen grains per flower and number of ovules have been traditionally
associated with the type of incompatibility system where species with
higher pollen ovule ratios are predicted to be xenogamous and species
with low pollen ovule ratios autogamous (REF). Selfer species are known
to have a reduction of herkogamy (REF) and less pollen production per
ovule (REF) which can be interpretated as a reduction of pollen exported
into the community. Other morphological traits, like stigma size can be
determinant for the total pollen quatity that a stigma can receive and
therefore related to do that pollen size would also play an important
role. Example with pollen here.

\href{Jose}{This last bit of the paragraph is still under development}

\textbf{Paragraph 4} Maybe connect with paragrph above?

\href{Romina}{Comments on it}

Species with similar traits are more closely related XXXXXXXXX. (Refs?
Brown and Mitchell (2001) Arceo-Gómez et al. (2016) Tong and Huang
(2016) ). Several studies predict that the impact of HP transfer is
likely to be greater for closely related species (Ashman and Arceo-Gómez
(2013)). Few studies however, have focused on the impacts of
heterospecific pollen of distantly related species Thomson et al. (1982)
Galen and Gregory (1989) Neiland and Wilcock (1999). Yet, most insects
and most stigmas have been found to carry multiple species of foreign
pollen with little attention to degree of relatedness (Arceo-Gómez and
Ashman (2016); Fang and Huang (2013) ; also cite studies from pollen
transfer networks here such as\ldots{} ). Further, a majority of plant
species are generalist and thus receive visits from multiple different
pollinators. Given these are generally the ones that receive greater
loads of heterospecific pollen Fang and Huang (2013) and unrelated
species are more likely to coexist with other species due to less niche
overlap (Ref), understanding the role of foreign pollen from distantly
related species thus deserves greater attention in understanding
coexistence blah blahXXXXX refs.. Notwithstanding, the effect of
heterospecific pollen of far and close related species at community
level remains to be explored beyond single pairwise interactions.

\textbf{Paragraph 5} Introducing our experiment

@@

We used the statistical language \texttt{R} (R Core Team 2018) for all
our analyses. Differences of seed set between treatments and hand cross
pollination for each species was tested through mixed linear models. For
the following analysis we scaled the values of seed production for all
the species with mean 0 and sd of 1. To test the effect of
heterospecific pollen, we substracted to the seed set of hand cross
pollination the seed set of heterospecific pollen treatments. In order
to see correlations between heterospecific pollen effect and traits we
performed Mantel test between the matrix of heterospecific pollen effect
and the distance matrix of each trait (euclidean distances). Moreover,
Mantel test was also conducted between heterospecific pollen effect and
the square root of the matrix of phylogenetic distance due to
improvement in the statistical power (Letten \& Cornwell 2014). We
explored also the the relations between traits and heterospecific pollen
effect through generalized mixed models where the response variable was
heterospecific pollen effect, the independent variable the different
traits and the random effects the different treatments per species.
Moreover, pairwise evolutive distances were calculated with MEGA7 for
two kinds of markers: 1) Internal transcribed spacer (ITS) and 2)
ribulose-bisphosphate carboxylase (RBCL). The sequences of interest were
downloaded from NCBI GenBank and the phylogenetic tree constructed by
maximum likelihood with MEGA7.

\href{Jose}{Phylogenetic signal of traits?}

@@

Results of hand cross pollination, self hand pollination, natural
selfing and apomixis are presented in \textbf{Table 2}. Heterospecific
pollen reduced seet set signifcatively with the 50-50\% heterospecific
pollen treatments for 65\% of the pairwise interactions
p\textless{}0.05. Across families we found a very similar effect but
when species where look at species level they respond differently even
within the same family, for instance for two species of the Brassicaceae
family \emph{Brassica oleracea} and \emph{Eruca versicaria} we found
very contrasting effects of foreign pollen where for the first one, all
donors reduce seed set significatively and for the second, just two
species did out of nine. The 100\% foreign pollen treatments barely
produced seeds or fruits and just for \emph{Sinapis alba} we did not
find significant differences between the hand cross pollination and one
treatment with pollen from a confamilial. Solanaceae species with berry
fruit type developed small fruits or even normal fruits in some cases.
\emph{S. lycopersicum} seems to produced small fruits (35\% of the
treatments) independently of pollen and pollen donor due to also
apomictic treatments did, never normal size. \emph{C. annuum} produced
some fruits (9\%) of both small and normal size and finally \emph{S.
melongena} produced seedless normal fruits with just confamilial pollen
(3\%), for both species seems that fruit formation was induced by pollen
on the stigma because of lack of fruit production with treatments that
tested for apomixis.

@@

Mantel test indicates that a possible correlation exist between
heterospecific pollen effect and the evolutive distances, for ITS and
RBCL markers we had r coefficients of 0.29 and 0.25 respectively
p\textless{}0.05. Moreover, Mantel test indicates that also a possible
correlation between stigma width and stigma type exist. Trait
correlations were also explored with GLMM

\href{Jose}{I have done it at the moment just for Compatibility system}
\href{Jose}{Also I have to fix from mixed linear model to GLMM, just
realize that}

@@

\href{Jose}{Compatibility index don´t multiply per 100 from Lloyd}

@@

Other idea based on the paper of Aizen 2007:

He explains seed set in this way. O total number of ovules, d fraction
of ovules that become seed set, b proportion of pollen grains that reach
ovules, p number of pollen grains.

\(S=dO(1-e^bp)\)

\(S=dO(1-e^bp(HpEffect))\)

but this Hp effect maybe can be divided at the same time in the
interaction between recipient-donor with the main traits that drive the
effect. Moreover, this should consider quantity of hp. lINEAR EFFECT?
How to model this maybe talk with nacho.

@@
